---
title: "Loading The ECD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Loading_The_ECD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ecdata)
library(dplyr)
```

The Executive Communcations Dataset (ECD) is a dataset comprised of executive communications across 41 differenct countries. The `ecdata` package is a minimal package to download data from the ecd repositories. It includes caching and data dicitionaries. 

## `load_ecd`

The default function for loading the ECD is `load_ecd`. This function will download data from our repositories and load them into memory. You can load the full ECD by setting `load_ecd(full_ecd = TRUE)` This can take awhile because you are downloading a `1.9GB` parquet file.  


```{r}

full_ecd = load_ecd(full_ecd = TRUE) 

head(full_ecd)

```


If you want a specific country or countries you can feed a character vector to the `country` argument. 


```{r}

load_ecd(country = 'Greece')

```

The country argument tolerates some typos, common abbreviations, and common country names. 



```{r}

load_ecd(country = 'united states')

load_ecd(country = 'UK')

```