---
title: "Loading_The_ECD"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Loading_The_ECD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ecdata)

```

The Executive Communcations Dataset (ECD) is a dataset comprised of executive communications across 41 differenct countries. The `ecdata` package is a minimal package to download data from the ecd repositories. It includes caching and data dicitionaries. 

## `load_ecd`

The default function for loading the ECD is `load_ecd`. This function will download data from our repositories and load them into memory. You can load the full ECD by setting `load_ecd(full_ecd = TRUE)` This can take awhile because you are downloading a `1.9GB` parquet file.  


```{r load-full-ecd, eval = FALSE}

full_ecd = load_ecd(full_ecd = TRUE) 



```


If you want a specific country or countries you can feed a character vector to the `country` argument. 


```{r}

load_ecd(country = 'Greece')

```

The country argument tolerates some typos, common abbreviations, and common country names. 



```{r}

load_ecd(country = 'south korea')

load_ecd(country = 'Nz')

```


Note that the time to download and load a file will vary a lot due to various file sizes. 

If instead you want a specific language or languages you can set a language option to your query using the `language` argument. 



```{r}

load_ecd(language = 'Turkish')

```

This will only load data for a specific language. In this case this is equivalent of setting `country = 'Turkey'` however, for English, Spanish, German, and Portugese will load data from multiple countries. 


## `lazy_load_ecd`

We also have a "lazy" option which will download the files and then use `arrow::open_dataset` to open the dataset out of memory. 


```{r}

nigeria = lazy_load_ecd(country = 'Nigeria')



```


To bring the dataset into memory you simply need to call. 

```{r}

nigeria |>
  dplyr::collect()

```

This has some speed benefits when data wrangling. One thing to be aware of is that if you lazy load a dataset previously it may bring in additional files. To prevent this behavior run 



```{r eval = FALSE}

clear_cache()

```

Then restart your R session.