---
title: "Loading_The_ECD"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Loading_The_ECD}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

In this vignette I introduce you to the basic functions of the `ecdata` package. You can download the latest stable releases of the packages through CRAN and PyPi 

```{r}
library(ecdata)
library(dplyr)

```



### `load_ecd`

The primary function that is shared across the Python and R distributions of the package is the `load_ecd` function. This function accepts four primary arguments:


```{r}
#| echo: false

tibble::tribble(~'Argument', ~`R Specific Quirks`, ~`Python Specific Quirks`, 
                            'country', 'A String/A String Vector', 'String, Dictionary, or List',
                            'language',  'A String/A String Vector', 'String, Dictionary, or List',
                            'full_ecd', 'A boolean if set to TRUE downloads full dataset. Defaults to FALSE', 'A boolean if set to True downloads full dataset. Defaults to False',
                            'ecd_version', 'A character string of the ECD version you want to download. Defaults to latest version', 'A character string of the ECD version you want to download. Defaults to latest version') |>
                                tinytable::tt()


```

Functionally the `ecd_version` argument is not entirely useful since there has only been one release of the data. 


Say we only wanted data for South Korea^[I choose South Korea because the underlying file is relatively small compared to some of the other country files.] we can simply set the country argument like this: 


```{r}

rok = load_ecd(country = 'Republic of Korea')

head(rok, 2)

```


We implement caching by default so you will get a pretty shouty warning every few hours in R. `load_ecd` has some tolerance for common names, abbreviations, and mixed punctuations of countries so if we wanted to download the same data using `KR`, `KOR`, or `South Korea` these will all download the South Korean data. 


### R 

```{r}

sk = load_ecd(country = 'South Korea')

```


The same functionality is extended to the language argument too!


### Schema and duplicate handling

The published country files do not all carry the same columns, and `date` is a
plain date in two of them and a UTC timestamp in the rest. `load_ecd` puts every
file onto the 17 documented columns before combining them, so a multi country
call returns one rectangle no matter which countries you ask for. Pass
`normalize_schema = FALSE` if you would rather have the columns exactly as they
are published.

Several country files repeat the same statement many times over: about 99% of the
rows in `india.parquet` and `denmark.parquet` are exact duplicates. Row counts
match the published files by default. Pass `deduplicate = TRUE` to drop rows that
repeat on url, text and date.

```{r}
#| eval: false

india = load_ecd(country = 'India', deduplicate = TRUE)

```

`load_ecd` warns you when you load a file with a known problem in it. The full
list of known problems in release 1.0.0, and the script that finds them, are in
[`data-validation/`](https://github.com/Executive-Communications-Dataset/ecdata/tree/main/data-validation)
in the package repository.
